---
title: "Table_emily"
author: "Emily Lu"
date: "2023-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
library(reshape2)
library(ggpubr)
```


## Making Table

### In-sample Performance

#### LOSO

```{r}
datasets <- c("Dataset 1", "Dataset 7") #creating a vector for iterating over datasets
Threshold <- c(0.33, 0.45) #creating a vector of thresholds respectively
```

```{r}
## rearrange the data
data1 <- data.frame("Dataset" = rep("Dataset 1", 5707), "Site" = modelData$SiteNo, "dengue" = modelData$dengue, "Age" = modelData$Age, "WBC" = modelData$WBC, "PLT" = modelData$PLT)

data7 <-  data.frame("Dataset" = rep("Dataset 7", 1485), "Site" = dengue7$Site, "dengue" = dengue7$dengue, "Age" = dengue7$Age, "WBC" = dengue7$WBC, "PLT" = dengue7$PLT)

LOSO <- rbind(data1, data7)
```

```{r}
## making data frame to store the data
loso_result <- data.frame("Dataset" = rep(NA, 2),"Threshold" = rep(NA,2), "Sensitivity" = rep(NA, 2), "Specificity" = rep(NA, 2), "PPV" = rep(NA, 2), "NPV" = rep(NA, 2), "AUC" = rep(NA, 2))
```

```{r}

for (i in seq(1, length(datasets), by = 1)){
  
  data <- LOSO[which(LOSO$Dataset == datasets[i]), ] #extract one dataset a time
  
  #store corresponding information into the table
  loso_result$Dataset[i] <- datasets[i]
  loso_result$Threshold[i] <- Threshold[i]
  
  #creating vector for iteration
  site <- unique(data$Site)
  site <- as.factor(site)
  
  YHat <-  rep("NA", nrow(data))
  
  for(j in site){
  
    f <- which(data$Site == j)
  
    losoTrain <- data[-f,] #creating train and test data
    losoTest <- data[f,]
  
    bm <- glm(dengue ~ Age + WBC + PLT, data=losoTrain, family=binomial)
  
    YHat[f] <- predict(bm, newdata = losoTest, type = "resp") #store the prediction
  
  }
  
  YHat <- as.numeric(YHat)
  
  loso_prob <- ifelse(YHat > Threshold[i], 1, 0)
  
  ## preparing for metric calculation
  true1 <- which(data$dengue == 1)
  true0 <- which(data$dengue == 0)
  
  loso_pred1 <- which(loso_prob == 1)
  loso_pred0 <- which(loso_prob == 0)

  ntrue1 <- length(true1)
  ntrue0 <- length(true0)
  
  ##store and calculate desired metrics into the table
  loso_result$Sensitivity[i] <- (length(which(loso_prob[true1] == 1)))/ntrue1
  loso_result$Specificity[i] <- (length(which(loso_prob[true0] == 0)))/ntrue0
  loso_result$PPV[i] <- (length(which(data$dengue[loso_pred1] == 1)))/(length(loso_pred1))
  loso_result$NPV[i] <- (length(which(data$dengue[loso_pred0] == 0)))/(length(loso_pred0))
    
  
  roc <- prediction(YHat, data$dengue)
  auc <- performance(roc, measure = "auc")
  loso_result$AUC[i] <- auc@y.values
  
}
```

#### 10-fold cross-validation
```{r}
## rearrange the data
data10 <-  data.frame("Dataset" = rep("Dataset 10", 1552), "dengue" = dengue10$dengue, "Age" = dengue10$Age, "WBC" = dengue10$WBC, "PLT" = dengue10$PLT)

data13_d1 <- data.frame("Dataset" = rep("Dataset 13 Day 1", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_1, "PLT" = clean13$plt_1)

data13_d3 <- data.frame("Dataset" = rep("Dataset 13 Day 3", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_3, "PLT" = clean13$plt_3)

data17 <- data.frame("Dataset" = rep("Dataset 17", 368), "dengue" = dengue17$dengue, "Age" =  dengue17$Age, "WBC" = dengue17$WBC, "PLT" = dengue17$PLT)

cv <- rbind(data10, data13_d1, data13_d3, data17)
```

```{r}
datasets <- c("Dataset 10", "Dataset 13 Day 1", "Dataset 13 Day 3", "Dataset 17") #creating a vector for iterating over datasets
Threshold <- c(0.21, 0.64, 0.59,0.43) #creating a vector of thresholds respectively
```

```{r}
## making data frame to store the data
cv_result <- data.frame("Dataset" = rep(NA, 4),"Threshold" = rep(NA, 4), "Sensitivity" = rep(NA, 4), "Specificity" = rep(NA, 4), "PPV" = rep(NA, 4), "NPV" = rep(NA, 4), "AUC" = rep(NA, 4))
```


```{r}
set.seed(1) # set seed for reproducibility

for (i in seq(1, length(datasets), by = 1)){
  
  data <- cv[which(cv$Dataset == datasets[i]), ] # extract one dataset a time
  
  #store corresponding information into the table
  cv_result$Dataset[i] <- datasets[i] 
  cv_result$Threshold[i] <- Threshold[i]
  
  ## creating folds
  pool <- rep(1:10, ceiling(nrow(data)/10)) 
  folds <- sample(pool, nrow(data))
  
  YHat <-  rep("NA", nrow(data))
  
  for(j in 1:10){
  
    f <- which(folds == j)
  
    cvTrain <- data[-f,]
    cvTest <- data[f,]
  
    bm <- glm(dengue ~ Age + WBC + PLT, data=cvTrain, family=binomial)
  
    YHat[f] <- predict(bm, newdata = cvTest, type = "resp")
  
  }
  
  YHat <- as.numeric(YHat)
  
  cv_prob <- ifelse(YHat > Threshold[i], 1, 0)
  
  ## preparing for metric calculation
  true1 <- which(data$dengue == 1)
  true0 <- which(data$dengue == 0)
  
  cv_pred1 <- which(cv_prob == 1)
  cv_pred0 <- which(cv_prob == 0)

  ntrue1 <- length(true1)
  ntrue0 <- length(true0)
  
  ##store and calculate desired metrics into the table
  cv_result$Sensitivity[i] <- (length(which(cv_prob[true1] == 1)))/ntrue1
  cv_result$Specificity[i] <- (length(which(cv_prob[true0] == 0)))/ntrue0
  cv_result$PPV[i] <- (length(which(data$dengue[cv_pred1] == 1)))/(length(cv_pred1))
  cv_result$NPV[i] <- (length(which(data$dengue[cv_pred0] == 0)))/(length(cv_pred0))
    
  roc <- prediction(YHat, data$dengue)
  auc <- performance(roc, measure = "auc")
  cv_result$AUC[i] <- auc@y.values
  
}
```

```{r}
## combining all the results into one table
in_sample <- rbind(loso_result, cv_result)
in_sample$AUC <- as.numeric(in_sample$AUC)
```

```{r}
## round the result for better readability
in_sample_round3 <- in_sample %>%                  
                 mutate_if(is.numeric,
                           round,
                           digits = 3)


## making table
knitr::kable(in_sample_round3,
            caption = "In-Sample Performance of Each Dataset")
```



## Making Table (Generalization)

```{r}
## rearrange the data
data1 <- data.frame("Dataset" = rep("Dataset 1", 5707), "dengue" = modelData$dengue, "Age" = modelData$Age, "WBC" = modelData$WBC, "PLT" = modelData$PLT)

data7 <-  data.frame("Dataset" = rep("Dataset 7", 1485), "dengue" = dengue7$dengue, "Age" = dengue7$Age, "WBC" = dengue7$WBC, "PLT" = dengue7$PLT)

data10 <-  data.frame("Dataset" = rep("Dataset 10", 1552), "dengue" = dengue10$dengue, "Age" = dengue10$Age, "WBC" = dengue10$WBC, "PLT" = dengue10$PLT)

data13_d1 <- data.frame("Dataset" = rep("Dataset 13 Day 1", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_1, "PLT" = clean13$plt_1)

data13_d3 <- data.frame("Dataset" = rep("Dataset 13 Day 3", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_3, "PLT" = clean13$plt_3)

data17 <- data.frame("Dataset" = rep("Dataset 17", 368), "dengue" = dengue17$dengue, "Age" =  dengue17$Age, "WBC" = dengue17$WBC, "PLT" = dengue17$PLT)

data <- rbind(data1, data7, data10, data13_d1, data13_d3, data17)
```

```{r}
## create a dataframe to store final results
Result <- data.frame("Train" = rep(NA, 60), "Test" = rep(NA, 60), "Threshold" = rep(NA, 60), "Sensitivity" = rep(NA, 60), "Specificity" = rep(NA, 60), "PPV" = rep(NA, 60), "NPV" = rep(NA, 60), "AUC" = rep(NA, 60))

## create vectors for iteration
datasets <- c("Dataset 1", "Dataset 7", "Dataset 10", "Dataset 13 Day 1", "Dataset 13 Day 3", "Dataset 17")
t <- c(0.33, 0.45, 0.21, 0.71, 0.62,0.43)

Threshold <- data.frame(datasets, t)

m <- 1 # initialize the index parameter

for (i in 1:length(datasets)){
  Train <- data[which(data$Dataset == datasets[i]), ] # use one dataset as training dataset a time
  t1 <- Threshold$t[i] # get the threshold
  
  ## create new, temporary vectors that only exclude the information of the selected training dataset
  new_datasets <- datasets[-i]
  new_t <- Threshold[-i,]
  
  for (j in 1:length(new_datasets)){
    Test <- data[which(data$Dataset == new_datasets[j]),] # extract one dataset as test dataset a time
    t2 <- new_t$t[j] # get the threshold
    
    ## store corresponding information into the table
    Result$Train[m] <- datasets[i]
    Result$Test[m] <- new_datasets[j]
    Result$Threshold[m] <- t1
    
    model <- glm(dengue ~ Age + WBC + PLT, data=Train, family=binomial)
    YHat <- predict(model, newdata = Test, type = "resp")
    
    ## preparing for metric calculation
    prob_t1 <- ifelse(YHat > t1, 1, 0)
    prob_t2 <- ifelse(YHat > t2, 1, 0)

    pred1_t1 <- length(which(prob_t1 == 1))
    pred0_t1 <- length(which(prob_t1 == 0))

    True1 <- which(Test$dengue == 1)
    True0 <- which(Test$dengue == 0)

    nTrue1 <- length(True1)
    nTrue0 <- length(True0)
    
    ## calculate and store the desired metrics using the first threshold (threshold of the training data)
    Result$Sensitivity[m] <- (length(which(prob_t1[True1] == 1)))/nTrue1
    Result$Specificity[m] <- (length(which(prob_t1[True0] == 0)))/nTrue0
    Result$PPV[m] <- (table(prob_t1, Test$dengue)[2,2])/pred1_t1
    Result$NPV[m] <- (table(prob_t1, Test$dengue)[1,1])/pred0_t1
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    Result$AUC[m] <- auc@y.values
    
    m <- m+1 ## updating the index parameter
    
    ## preparing for metric calculation
    pred1_t2 <- length(which(prob_t2 == 1))
    pred0_t2 <- length(which(prob_t2 == 0))
    
    ## calculate and store the desired metrics using the second threshold (threshold of the test data)
    Result$Train[m] <- datasets[i]
    Result$Test[m] <- new_datasets[j]
    Result$Threshold[m] <- t2
    Result$Sensitivity[m] <- (length(which(prob_t2[True1] == 1)))/nTrue1
    Result$Specificity[m] <- (length(which(prob_t2[True0] == 0)))/nTrue0
    Result$PPV[m] <- (table(prob_t2, Test$dengue)[2,2])/pred1_t2
    Result$NPV[m] <- (table(prob_t2, Test$dengue)[1,1])/pred0_t2
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    Result$AUC[m] <- auc@y.values
    
    m <- m+1 # update the index parameter
    
  }
  
  
}

Result$AUC <- as.numeric(Result$AUC)

Result <- Result[-c(37:38, 47:48),] # remove the redundant rows
rownames(Result)[1:56] <- c(1:56) # reorder the rows after removal
```


```{r}
## round the result for better readability
Result_round3 <- Result %>%                  
                 mutate_if(is.numeric,
                           round,
                           digits = 3)

## making the table using the dataframe
knitr::kable(Result_round3,
            caption = "Comparison of Predictive Performance among Different Datasets")
```


### Making Filtering Age Table

```{r}
## making substes from data7 and data10
child7 <- dengue7 %>%
  filter(dengue7$Age <= 15)

child10 <- dengue10 %>%
  filter(dengue10$Age <= 15)

adult7 <- dengue7 %>%
  filter(dengue7$Age >= 17)

adult10 <- dengue10 %>%
  filter(dengue10$Age >= 17)

## rearrange the data
child_data7 <- data.frame("Dataset" = rep("Dataset 7", 518), "dengue" = child7$dengue, "Age" = child7$Age, "WBC" = child7$WBC, "PLT" = child7$PLT)

child_data10 <- data.frame("Dataset" = rep("Dataset 10", 571), "dengue" = child10$dengue, "Age" = child10$Age, "WBC" = child10$WBC, "PLT" = child10$PLT)


adult_data7 <- data.frame("Dataset" = rep("Dataset 7", 900), "dengue" = adult7$dengue, "Age" = adult7$Age, "WBC" = adult7$WBC, "PLT" = adult7$PLT)

adult_data10 <- data.frame("Dataset" = rep("Dataset 10", 946), "dengue" = adult10$dengue, "Age" = adult10$Age, "WBC" = adult10$WBC, "PLT" = adult10$PLT)
```

#### Filtering out adults data (children only)
```{r}
## making table to store the result
child <- data.frame("Train" = rep(NA, 12), "Test" = rep(NA, 12), "Threshold" = rep(NA, 12), "Sensitivity" = rep(NA, 12), "Specificity" = rep(NA, 12), "PPV" = rep(NA, 12), "NPV" = rep(NA, 12), "AUC" = rep(NA, 12))
```

```{r}
child_data <- rbind(data1, data13_d1, data13_d3)

## making vectors to store the information of dataset and threshold
datasets <- c("Dataset 1","Dataset 13 Day 1","Dataset 13 Day 3")
t <- c(0.33,0.71, 0.62)
c <- c(0.45,0.21)

m <- 1 # initialize the index parameter

for (i in 1:length(datasets)){
  
  Train <- child_data[which(child_data$Dataset == datasets[i]), ] # use one dataset as training dataset a time
  
  child[m:(m+3), "Train"] <- datasets[i] # store the dataset name in the final table
  
  t1 <- t[i] # get the threshold of the training dataset
  
  
  for (j in 1:length(c)){
    
    ## extract and store the corresponding information into the final table
    if (j == 1){
      Test <- child_data7
      t2 <- c[j]
      child[m:(m+1), "Test"] <- "Dataset 7"
    }
    else{
      Test <- child_data10
      t2 <- c[j]
      child[m:(m+1), "Test"] <- "Dataset 10"
    }
    
    model <- glm(dengue ~ Age + WBC + PLT, data=Train, family=binomial)
    YHat <- predict(model, newdata = Test, type = "resp")
    
    ## prepare for the metric calculation
    prob_t1 <- ifelse(YHat > t1, 1, 0)
    prob_t2 <- ifelse(YHat > t2, 1, 0)
    
    pred1_t1 <- length(which(prob_t1 == 1))
    pred0_t1 <- length(which(prob_t1 == 0))

    True1 <- which(Test$dengue == 1)
    True0 <- which(Test$dengue == 0)

    nTrue1 <- length(True1)
    nTrue0 <- length(True0)
    
    ## calculate and store the desired metrics using the first threshold (threshold of the training data)
    child$Threshold[m] <- t1
    child$Sensitivity[m] <- (length(which(prob_t1[True1] == 1)))/nTrue1
    child$Specificity[m] <- (length(which(prob_t1[True0] == 0)))/nTrue0
    child$PPV[m] <- (table(prob_t1, Test$dengue)[2,2])/pred1_t1
    child$NPV[m] <- (table(prob_t1, Test$dengue)[1,1])/pred0_t1
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    child$AUC[m] <- auc@y.values
    
    m <- m+1 # update the index paramter
    
    ## prepare for the metric calculation
    pred1_t2 <- length(which(prob_t2 == 1))
    pred0_t2 <- length(which(prob_t2 == 0))
    
    ## calculate and store the desired metrics using the second threshold (threshold of the test data)
    child$Threshold[m] <- t2
    child$Sensitivity[m] <- (length(which(prob_t2[True1] == 1)))/nTrue1
    child$Specificity[m] <- (length(which(prob_t2[True0] == 0)))/nTrue0
    child$PPV[m] <- (table(prob_t2, Test$dengue)[2,2])/pred1_t2
    child$NPV[m] <- (table(prob_t2, Test$dengue)[1,1])/pred0_t2
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    child$AUC[m] <- auc@y.values
    
    m <- m+1 # update the index paramter
    
  }
  
  
}

child$AUC <- as.numeric(child$AUC)
```


#### Filtering out adult data (adult only)
```{r}
## create a dataframe to store the result
adult <- data.frame("Train" = rep(NA, 12), "Test" = rep(NA, 12), "Threshold" = rep(NA, 12), "Sensitivity" = rep(NA, 12), "Specificity" = rep(NA, 12), "PPV" = rep(NA, 12), "NPV" = rep(NA, 12), "AUC" = rep(NA, 12))
```

```{r}
adult_data <- rbind(adult_data7, adult_data10, data17)

## making vectors to store the information of dataset and threshold
datasets <- c("Dataset 7", "Dataset 10", "Dataset 17")
t <- c(0.45,0.21,0.43)

m <- 1 ## initialize index parameter

for (i in 1:length(datasets)){
  
  Train <- adult_data[which(adult_data$Dataset == datasets[i]), ] # use one dataset as training dataset a time
  t1 <- t[i] # get the threshold for the training dataset
  
  ## create new, temporary vectors that only exclude the information of the selected training dataset
  new_datasets <- datasets[-i]
  new_t <- t[-i]
  
  for (j in 1:length(new_datasets)){
    Test <- adult_data[which(adult_data$Dataset == new_datasets[j]),] # extract one dataset as test dataset
    t2 <- new_t[j] # get the threshold for the test dataset
    
    ## store the corresponding information into the table
    adult$Train[m] <- datasets[i]
    adult$Test[m] <- new_datasets[j]
    adult$Threshold[m] <- t1
    
    model <- glm(dengue ~ Age + WBC + PLT, data=Train, family=binomial)
    YHat <- predict(model, newdata = Test, type = "resp")
    
    ## prepare for metric calculation
    prob_t1 <- ifelse(YHat > t1, 1, 0)
    prob_t2 <- ifelse(YHat > t2, 1, 0)

    pred1_t1 <- length(which(prob_t1 == 1))
    pred0_t1 <- length(which(prob_t1 == 0))

    True1 <- which(Test$dengue == 1)
    True0 <- which(Test$dengue == 0)

    nTrue1 <- length(True1)
    nTrue0 <- length(True0)
    
    ## store and calculate the desired metrics
    adult$Sensitivity[m] <- (length(which(prob_t1[True1] == 1)))/nTrue1
    adult$Specificity[m] <- (length(which(prob_t1[True0] == 0)))/nTrue0
    adult$PPV[m] <- (table(prob_t1, Test$dengue)[2,2])/pred1_t1
    adult$NPV[m] <- (table(prob_t1, Test$dengue)[1,1])/pred0_t1
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    adult$AUC[m] <- auc@y.values
    
    m <- m+1 # update the index parameter
    
    ## prepare for metric calculation
    pred1_t2 <- length(which(prob_t2 == 1))
    pred0_t2 <- length(which(prob_t2 == 0))
    
    ## store and calculate the desired metrics
    adult$Train[m] <- datasets[i]
    adult$Test[m] <- new_datasets[j]
    adult$Threshold[m] <- t2
    adult$Sensitivity[m] <- (length(which(prob_t2[True1] == 1)))/nTrue1
    adult$Specificity[m] <- (length(which(prob_t2[True0] == 0)))/nTrue0
    adult$PPV[m] <- (table(prob_t2, Test$dengue)[2,2])/pred1_t2
    adult$NPV[m] <- (table(prob_t2, Test$dengue)[1,1])/pred0_t2
    
    roc <- prediction(YHat, Test$dengue)
    auc <- performance(roc, measure = "auc")
    adult$AUC[m] <- auc@y.values
    
    m <- m+1 # update the index parameter
    
    
  }
  
  
}
  

adult <- adult[-c(1:8),] # remove the redundant rows
rownames(adult)[1:nrow(adult)] <- c(1:nrow(adult)) # reorder the rownames
```

```{r}
## combine the results into one dataframe
Filter <- rbind(child,adult)
Filter <- as.data.frame(Filter)
Filter$AUC <- as.numeric(Filter$AUC)
rownames(Filter)[1:nrow(Filter)] <- c(1:nrow(Filter)) # reorder the rownames
```



```{r}
## round the result for better readability
Filter_round3 <- Filter %>%                  
                 mutate_if(is.numeric,
                           round,
                           digits = 3)

## making table
knitr::kable(Filter_round3,
            caption = "Comparison of Predictive Performance among Different Datasets, controlling age")
```


## Making plot
```{r}
## create a dataframe for sotring the information needed for plotting
plot <- data.frame("Train" = rep(NA, 28), "Test" = rep(NA, 28), "Threshold" = rep(NA, 28), "Sensitivity" = rep(NA, 28), "Specificity" = rep(NA, 28), "PPV" = rep(NA, 28), "NPV" = rep(NA, 28), "AUC" = rep(NA, 28))

## extract the information from the in-sample performance table
for (i in seq(1, nrow(Result), by = 2)){
  
  for(j in seq(1, ncol(Result), by = 1)){
    plot[i,j] <- Result[i,j]
  }
}
```

```{r}
plot_AUC$Train <- as.factor(plot_AUC$Train)
```

### Making plot for each dataset's generalizing performance separately (AUC comparison plot)
```{r}
plot_Train1 <- plot_AUC[which(plot_AUC$Train == "Dataset 1"),] # extract the information

## order the test dataset in ascending order
plot_Train1$Test <- factor(plot_Train1$Test, levels = plot_Train1$Test) 
t1 <- plot_Train1 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") +
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 1)")

t1
```



```{r}
plot_Train7 <- plot_AUC[which(plot_AUC$Train == "Dataset 7"),]
plot_Train7$Test <- factor(plot_Train7$Test, levels = plot_Train7$Test)
t7 <- plot_Train7 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") +
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 7)")

t7
```

```{r}
plot_Train10 <- plot_AUC[which(plot_AUC$Train == "Dataset 10"),]
plot_Train10$Test <- factor(plot_Train10$Test, levels = plot_Train10$Test)
t10 <- plot_Train10 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") + 
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 10)")

t10
```

```{r}
plot_Train13_d1 <- plot_AUC[which(plot_AUC$Train == "Dataset 13 Day 1"),]
plot_Train13_d1$Test <- factor(plot_Train13_d1$Test, levels = plot_Train13_d1$Test)
td1 <- plot_Train13_d1 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") +
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 13 (Day 1))")

td1
```

```{r}
plot_Train13_d3 <- plot_AUC[which(plot_AUC$Train == "Dataset 13 Day 3"),]
plot_Train13_d3$Test <- factor(plot_Train13_d3$Test, levels = plot_Train13_d3$Test)
td3 <- plot_Train13_d3 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") +
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 13 (Day 3))")

td3 
```

```{r}
plot_Train17 <- plot_AUC[which(plot_AUC$Train == "Dataset 17"),]
plot_Train17$Test <- factor(plot_Train17$Test, levels = plot_Train17$Test)
t17 <- plot_Train17 %>%
  ggplot(aes(x = Test, y = AUC, color =Test, group = 1)) +
  geom_point(cex = 3.5) + geom_line(color = "black") + 
  labs(x = "Test Datasets" , y = "AUC values (Trained on Dataset 17)")

t17
```


```{r}
## combining the plot made above into one graph
result_AUC <- ggarrange(t1, t7, t10, td1, td3, t17,
                    ncol = 2, nrow = 3)

result_AUC
```



## Plot for Filtered Data

```{r}
## create a dataframe to store the required information to make the plot
filter<- data.frame("Train" = rep(NA, 12), "Test" = rep(NA, 12), "Threshold" = rep(NA, 12), "Sensitivity" = rep(NA, 12), "Specificity" = rep(NA, 12), "PPV" = rep(NA, 12), "NPV" = rep(NA, 12), "AUC" = rep(NA, 12))

## extract the information from the table
for (i in seq(1, nrow(Filter))){
  
  for(j in seq(1, ncol(Filter), by = 1)){
   filter[i,j] <- Filter[i,j]
  }
}

filter_AUC <- drop_na(filter)
```

### Childen Subsets:

#### Train on Dataset 1
```{r}
## get the information for the plot we want to make
filter1_33 <- which(Filter$Train == "Dataset 1" & Filter$Threshold == 0.33)
filtered_data1_33 <- Filter[filter1_33,]
filtered_data1_33$Category = rep("Filtered", 2)
filtered_data1_33 <- filtered_data1_33[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

result1_33 <- which(Result$Train == "Dataset 1" & Result$Threshold == 0.33 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_data1_33 <- Result[result1_33 ,]
unfiltered_data1_33$Category = rep("Unfiltered", 2)
unfiltered_data1_33 <- unfiltered_data1_33[,-c(1,3,6,7)]

all_data1_33 <- rbind(filtered_data1_33, unfiltered_data1_33)

# reshape data for ggplot
melted1_33 <- melt(all_data1_33, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_metlted1_33 <- melted1_33 %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_metlted1_33$Category <- factor(ordered_metlted1_33$Category, levels = c("Unfiltered", "Filtered"))
ordered_metlted1_33$Test <- factor(ordered_metlted1_33$Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
f1_33 <- ggplot(ordered_metlted1_33, aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 1 (Threshold = 0.33)", y = "Value", color = "Metric") 

f1_33 
```

```{r}
## get the information for the plot we want to make
filter1_other <- which(Filter$Train == "Dataset 1" & Filter$Threshold != 0.33)
filtered_data1_other <- Filter[filter1_other,]
filtered_data1_other$Category = rep("Filtered", 2)
filtered_data1_other <- filtered_data1_other[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

result1_other <- which(Result$Train == "Dataset 1" & Result$Threshold != 0.33 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_data1_other <- Result[result1_other,]
unfiltered_data1_other$Category = rep("Unfiltered", 2)
unfiltered_data1_other <- unfiltered_data1_other[,-c(1,3,6,7)]

all_data1_other <- rbind(filtered_data1_other, unfiltered_data1_other)

# reshape data for ggplot
melted1_other <- melt(all_data1_other, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_metlted1_other <- melted1_other  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_metlted1_other$Category <- factor(ordered_metlted1_other$Category, levels = c("Unfiltered", "Filtered"))
ordered_metlted1_other$Test <- factor(ordered_metlted1_other$Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
f1_other <- ggplot(ordered_metlted1_other, aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 1 (Threshold = 0.45, Threshold = 0.21)", y = "Value", color = "Metric") 

f1_other
```


## Train on Day 1
```{r}
## get the information for the plot we want to make
filterdD1_71 <- which(Filter$Train == "Dataset 13 Day 1" & Filter$Threshold == 0.71)
filtered_dataD1_71 <- Filter[filterdD1_71,]
filtered_dataD1_71$Category = rep("Filtered", 2)
filtered_dataD1_71 <- filtered_dataD1_71[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

resultD1_71 <- which(Result$Train == "Dataset 13 Day 1" & Result$Threshold == 0.71 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_dataD1_71 <- Result[resultD1_71,]
unfiltered_dataD1_71$Category = rep("Unfiltered", 2)
unfiltered_dataD1_71 <- unfiltered_dataD1_71[,-c(1,3,6,7)]

all_dataD1_71 <- rbind(filtered_dataD1_71, unfiltered_dataD1_71)

# reshape data for ggplot
meltedD1_71 <- melt(all_dataD1_71, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_meltedD1_71  <-meltedD1_71  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_meltedD1_71 $Category <- factor(ordered_meltedD1_71 $Category, levels = c("Unfiltered", "Filtered"))
ordered_meltedD1_71 $Test <- factor(ordered_meltedD1_71 $Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
fd1_71 <- ggplot(ordered_meltedD1_71 , aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 13 Day 1 (Threshold = 0.71)", y = "Value", color = "Metric") 

fd1_71
```



```{r}
## get the information for the plot we want to make
filterD1_other <- which(Filter$Train == "Dataset 13 Day 1" & Filter$Threshold != 0.71)
filtered_dataD1_other <- Filter[filterD1_other,]
filtered_dataD1_other$Category = rep("Filtered", 2)
filtered_dataD1_other <- filtered_dataD1_other[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

resultD1_other <- which(Result$Train == "Dataset 13 Day 1" & Result$Threshold != 0.71 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_dataD1_other <- Result[resultD1_other,]
unfiltered_dataD1_other$Category = rep("Unfiltered", 2)
unfiltered_dataD1_other <- unfiltered_dataD1_other[,-c(1,3,6,7)]


all_dataD1_other <- rbind(filtered_dataD1_other, unfiltered_dataD1_other)

# reshape data for ggplot
meltedD1_other <- melt(all_dataD1_other, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_meltedD1_other <- meltedD1_other  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_meltedD1_other$Category <- factor(ordered_meltedD1_other$Category, levels = c("Unfiltered", "Filtered"))
ordered_meltedD1_other$Test <- factor(ordered_meltedD1_other$Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
fd1_other <- ggplot(ordered_meltedD1_other, aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 13 Day 1 (Threshold = 0.45, Threshold = 0.21)", y = "Value", color = "Metric") 

fd1_other
```


## Train on Day 3
```{r}
## get the information for the plot we want to make
filterdD3_62 <- which(Filter$Train == "Dataset 13 Day 3" & Filter$Threshold == 0.62)
filtered_dataD3_62 <- Filter[filterdD3_62,]
filtered_dataD3_62$Category = rep("Filtered", 2)
filtered_dataD3_62 <- filtered_dataD3_62[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

resultD3_62 <- which(Result$Train == "Dataset 13 Day 3" & Result$Threshold == 0.62 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_dataD3_62 <- Result[resultD3_62,]
unfiltered_dataD3_62$Category = rep("Unfiltered", 2)
unfiltered_dataD3_62 <- unfiltered_dataD3_62[,-c(1,3,6,7)]

all_dataD3_62 <- rbind(filtered_dataD3_62, unfiltered_dataD3_62)

# reshape data for ggplot
meltedD3_62 <- melt(all_dataD3_62, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_meltedD3_62  <-meltedD3_62  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_meltedD3_62$Category <- factor(ordered_meltedD3_62 $Category, levels = c("Unfiltered", "Filtered"))
ordered_meltedD3_62$Test <- factor(ordered_meltedD3_62 $Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
fd3_62 <- ggplot(ordered_meltedD3_62 , aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 13 Day 3 (Threshold = 0.62)", y = "Value", color = "Metric") 

fd3_62
```



```{r}
## get the information for the plot we want to make
filterdD3_other <- which(Filter$Train == "Dataset 13 Day 3" & Filter$Threshold != 0.62)
filtered_dataD3_other <- Filter[filterdD3_other,]
filtered_dataD3_other$Category = rep("Filtered", 2)
filtered_dataD3_other <- filtered_dataD3_other[,-c(1,3,6,7)] ## remove the columns that are not relevant to the plot

resultD3_other <- which(Result$Train == "Dataset 13 Day 3" & Result$Threshold != 0.62 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_dataD3_other <- Result[resultD3_other,]
unfiltered_dataD3_other$Category = rep("Unfiltered", 2)
unfiltered_dataD3_other <- unfiltered_dataD3_other[,-c(1,3,6,7)]

all_dataD3_other <- rbind(filtered_dataD3_other, unfiltered_dataD3_other)

# reshape data for ggplot
meltedD3_other <- melt(all_dataD3_other, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_meltedD3_other  <-meltedD3_other  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_meltedD3_other $Category <- factor(ordered_meltedD3_other $Category, levels = c("Unfiltered", "Filtered"))
ordered_meltedD3_other $Test <- factor(ordered_meltedD3_other $Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
fd3_other <- ggplot(ordered_meltedD3_other , aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 13 Day 3 (Threshold = 0.45, Threshold = 0.21)", y = "Value", color = "Metric") 

fd3_other
```


```{r}
## combining the plots made above into one graph
filter_child <- ggarrange(f1_33, f1_other, fd1_71,fd1_other, fd3_62, fd3_other,
                    ncol = 2, nrow = 3)

filter_child
```



```{r}
## get the information for the plot we want to make
filterd17 <- which(Filter$Train == "Dataset 17" & Filter$Threshold == 0.43)
filtered_data17 <- Filter[filterd17,]
filtered_data17$Category = rep("Filtered", 2)
filtered_data17 <- filtered_data17[,-c(1,3,6,7)] 

result17 <- which(Result$Train == "Dataset 17" & Result$Threshold == 0.43 & (Result$Test == "Dataset 7" | Result$Test == "Dataset 10"))
unfiltered_data17 <- Result[result17,]
unfiltered_data17$Category = rep("Unfiltered", 2)
unfiltered_data17 <- unfiltered_data17[,-c(1,3,6,7)]

all_data17 <- rbind(filtered_data17, unfiltered_data17)

# reshape data for ggplot
melted17 <- melt(all_data17, id.vars = c("Test", "Category"))

## to plot the data in order
cat_order <- c("Unfiltered", "Filtered")
test_order <- c("Dataset 7", "Dataset 10")
ordered_melted17 <-melted17  %>% 
  arrange(match(Category, cat_order), match(Test, test_order))
ordered_melted17$Category <- factor(ordered_melted17$Category, levels = c("Unfiltered", "Filtered"))
ordered_melted17$Test <- factor(ordered_melted17$Test, levels = c("Dataset 7", "Dataset 10"))

## plot using ggplot
## color choice are to be changed
f17 <- ggplot(ordered_melted17 , aes(x = Category, y = value, color = variable, group = variable)) +
  geom_line() +
  facet_wrap(~Test,  ncol=2) +
  scale_color_manual(values = c("Sensitivity" = "blue", "Specificity" = "purple", "AUC" = "red")) +
  labs(x = "Train: Dataset 13 Day 1 (Threshold = 0.71)", y = "Value", color = "Metric") 

f17
```


## Summary Table
```{r}
## pacakge needed for making table
install.packages("arsenal")
library(arsenal)
```

```{r}
## rearrange the data
data1 <- data.frame("Dataset" = rep("Dataset 1", 5707), "dengue" = modelData$dengue, "Age" = modelData$Age, "WBC" = modelData$WBC, "PLT" = modelData$PLT)

data7 <-  data.frame("Dataset" = rep("Dataset 7", 1485), "dengue" = dengue7$dengue, "Age" = dengue7$Age, "WBC" = dengue7$WBC, "PLT" = dengue7$PLT)

data10 <-  data.frame("Dataset" = rep("Dataset 10", 1552), "dengue" = dengue10$dengue, "Age" = dengue10$Age, "WBC" = dengue10$WBC, "PLT" = dengue10$PLT)

data13_d1 <- data.frame("Dataset" = rep("Dataset 13 Day 1", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_1, "PLT" = clean13$plt_1)

data13_d3 <- data.frame("Dataset" = rep("Dataset 13 Day 3", 257), "dengue" = clean13$dengue, "Age" =  clean13$Age, "WBC" = clean13$wbc_3, "PLT" = clean13$plt_3)

data17 <- data.frame("Dataset" = rep("Dataset 17", 368), "dengue" = dengue17$dengue, "Age" =  dengue17$Age, "WBC" = dengue17$WBC, "PLT" = dengue17$PLT)

data <- rbind(data1, data7, data10, data13_d1, data13_d3, data17)
```

```{r}
## create another dataset to make the table
test <- data
test$dengue <-as.factor(test$dengue)
```

```{r}
## rename datasets
for (i in seq(1,nrow(data), by=1)){
  if (test$Dataset[i] == "Dataset 7"){
    test$Dataset[i] = "Dataset 2"
  }
  if (test$Dataset[i] == "Dataset 10"){
    test$Dataset[i] = "Dataset 3"
  }
  if (test$Dataset[i] == "Dataset 13 Day 1"){
    test$Dataset[i] = "Dataset 4 Day 1"
  }
  if (test$Dataset[i] == "Dataset 13 Day 3"){
    test$Dataset[i] = "Dataset 4 Day 3"
  }
  if (test$Dataset[i] == "Dataset 17"){
    test$Dataset[i] = "Dataset 5"
  }
}
```


```{r}
## making table
sum_table <- tableby(Dataset~ ., data = test) 
summary(sum_table, title = "Summary Statistics")
```

```{r}
## customizing the statistics to include in the table
controls <- tableby.control(
  test=FALSE, 
  total=FALSE,
  numeric.stats = c("meansd", "medianq1q3", "range"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "Median",
    range = "Range"
  ),
  digits = 3
)

## customize the label of the table
labels <- list(
  dengue = "Dengue",
  Age = "Age",
  WBC = "White Blood Cell Count (WBC)",
  PLT = "Platelet Count (PLT)"
)
```


```{r}
## making the customized table
sum_two <- tableby(Dataset ~ .,
  data = test,
  control = controls
)

summary(sum_two,
  labelTranslations = labels,
  title = "Summary Statistic of All Datasets"
)
```


```{r}
## transforming it into a table
knitr::kable(summary(sum_two,
  labelTranslations = labels,
  title = "Summary Statistic of All Datasets",
  digits = 3
))
```



```{r}
## transform into dataframe for export (if needed)
df1 <- summary(sum_two,
  labelTranslations = labels,
  title = "Summary Statistic of All Datasets"
)

df_sum <- as.data.frame(df1)
```




























